### 2018-06-17 MSc_Marko_Docevski_tekst.tex
Updates from ShareLaTeX

\cite{Oord2016} Interesting way to reduce audio dimensionality. mu-law companding transformation They found that for audio signals tanh * sigmoid is a better activation function than ReLU WaveNET architecture Conditional WaveNETs a way of linking a part or the whole of the waveform to class or a characteristic. Eg a speaker in a multispeaker system or an instrument or composer. Local and global conditionings are possible. Context stacks are smaller nets the process a longer part of the audio and then locally condition the larger WaveNet that processes a smaller bit of the audio signal. They can have pooling layers to run at a lower frequency, to improve performance and decrease requirements. // Kind of like a hierarchy, but they needn't be stacked. Suggestion that a conditional WaveNet shares internal representation between different classes / conditionals. To capture longer term dependencies you need something more than just running the WaveNet over the data since it has a limited receptive size. MagnaTagATune dataset of 200hrs of music audio. Training on musical audio is tricky due to limited receptive size. Thins might be mitigated in symbolic music. They didn't get spectacular results on conditional WaveNets on the MagnaTagATune dataset because the tags was noisy. However after cleaning the tags up the results improved significantly. The generated music still has no long term musical structure.

@@

Eck et al. in \cite{Eck2002} describe the first application of deep learning to music generation. Due to the limited computational power at the time they defined a very simple experiment, generalization over 12 bar blues in written form, with a maximum of 8 notes per bar. They represented music in slices of note-time, i.e., one unit of time is \(\frac{1}{8}\)-th note long. This representation was later named as piano roll. The more complex of their two experiments consisted of learning in parallel a chord progression and a melody line, allowing them to generate both. Their architecture consists of 8 blocks of 2 LSTM cells, of which 4 are dedicated to learning melody the other 4 to learning the chord progression. The chords sections have output connections that influence the melody section but not vice versa. This work is the inspiration for most of the following research in the filed, including our own.

As an expansion to the previous work in \cite{Eck2008} Eck et al. improve their model by using musically important temporal information from the pieces, allowing it to learn structure at different granularities. The said information is metrically significant and is provided to the network as time-delayed copies of the network inputs at intervals that depend on the piece's meter. For pieces where no meter information is provided, the authors developed a technique for algorithmic meter extraction. The architecture consists of parallel LSTM layer and standard feed-forward layer, which is supposed to speed-up local dependency discovery. We plan to investigate how and whether having metrical information embedded into the learning model impacts performance.

The architectures presented in \cite{Hadjeres2016} and \cite{Liang2017} are specifically designed to tackle Bach chorales. A hybrid architecture was presented in \cite{Hadjeres2016} consisting of 2 LSTM subnets, of which one learns the sequence in standard order and the other in reverse order and a feed-forward subnet that learns the sequence in standard order. The three subnets are combined in a single feed-forward network. There is a copy of the architecture for each voice in the chorales. The music is generated by pseudo-Gibbs sampling procedure. They treat the 4 voices separately, as monophonic music generation problems, and combine them into a polyphonic melody. In contrast, we aim to generate mixture of chords/single notes from a single network output. To augment the dataset they transposed all the chorales to all transpositions that fit in the tonal range present in the corpus. We intend to do similar transposition schemes. The authors of \cite{Liang2017} approached the same problem with a 3-layer LSTM network, to which they applied Grid-search hyper-parameter tuning extensively to find optimal network and parameter configurations. They used a very different data representation, encoding all the voices in a single sequence, ordered by descending pitch.

Boulanger-Lewandowski et al. in \cite{Boulanger-Lewandowski2014} attempted to combine the RNNs' ability to model sequences and Restricted Boltzmann Machines' (RBMs) ability to model probability distributions and apply them to music generation, in an architecture dubbed RNN-RBM. In this architecture the RBM part models note co-occurrence probability distributions at each time-step and the RNN part models the temporal sequences. We aim to achieve polyphony by modeling  the probability of each output of the network independently of one another, even though realistically they are not, and try to avoid using a hybrid solution like RNN-RBN, due to it being difficult to train and computationally expensive.

In \cite{Johnson2017}, another hybrid deep learning model, the LSTM layers try to learn the temporal dependencies in the music, followed by a set of feed forward layers that try to learn note co-occurrences (or the harmonic part). They used a piano roll very similar to our own, enriched with additional meta-data extracted from the pieces.The meta-data depends on the music being of very regular form, which our dataset is no, so we did not include any.

The work presented in \cite{Bretan2016} approaches music generation as a word-level language model, where each unit (composed of 1 to 4 bars of music) is treated as word. The words are embedded in a descriptor vector. A library of word (or units) is then created from the complete set of embeddings. A LSTM network learns sequences of the embeddings. Music is generated by first sequencing embeddings, which are then decoded to actual note sequences by selecting the most appropriate representative out of the library of units. We used character level embeddings in out second experiment.

The implementation presented in \cite{Sturm2015} is very close to the one of \cite{AndrejKarpathy2015}. The authors transformed a set of folk songs in ABC notation into a modified version of the ABC notation that's more suitable for deep learning, that makes it very easy to unambiguously distinguish the various types of tokens, dubbed folk-rnn. On top of that they built a character-level model RNN deep learning model. Those tokens were encoded in one-hot vectors fed to 3 layer LSTM network, which outputs probability distribution over the unique token set. 
The authors of \cite{Madjiheurem2016} used an Auto-encoder architecture to learn chord latent space embeddings. A sequence learner model generalizes over sequences of latent space embeddings. They presented a comparison of several types of chord representations. One of the compared representations is very similar to what we used in our experiments. We discuss more in section VI.

\section{Пристап}

\section{Цел}

\subsection{Импровизации} 
\subsection{Помогната копозиција} 
\subsection{Самостојо генерирање}

>>>>

Во трудот \cite{Oord2016} дефинираат архитектура за обработка и учење на аудио сигнал со користење на конволуциски невронски мрежи, наречен WaveNet. Новоста во архитектурата се додадените временски дилатации и условеност на мрежата. Дилатациите функционираат на тој начин што временски задоцнети копии од податоците им се предаваат на повисоките слоеви во одредени интервали. Пр. влезниот слој обработува податоци од моменти: $t$, $t-1$, $t-2$ и $t-4$, следниот од $t$, $t-1$ и $t-2$, а последниот само од $t$ и $t-1$. Мрежата се улосував со пресметување на условни веројатности при извршување на конволуциите врз основа на класа на звук што се обработува, нпр. кој го изговара звучниот сегмент, на кој инструмент е отсвирен и тн. Архитектурата се покажала со ограничено рецептивно поле од околу $1/4$ од секунда, па учи мошне кратки секвенци, но тоа го прави многу добро. Најголем недостаток на самата архитектура е многу големата пресметковна цена, моделот го тренираат со недели на компјутерски кластер и му треба повеќе од час да генерира една секунда аудио сигнал, а времето расте со бројот на елементи во архитектурата (неврони по слој, број на слоеви).

@@

\section{Пристап}
\section{Цел}
\subsection{Импровизации} 
\subsection{Помогната копозиција} 
\subsection{Самостојо генерирање}
